### 2017-08-30 monograph/thesis/postexto/apendice_a.tex
Added the ufscthesis template files to the main document main.tex
Updated the pretexto remaining templates with ufscthesisx.

% ----------------------------------------------------------
\chapter[Anexo exemplo]{Como exibir o tamanho da fonte em uso na saída final}
% ----------------------------------------------------------

@@

1. How to display the font size in use in the final output,
2. How to display the font size in use in the final output,
3. How to display the font size in use in the final output,

@@

Lipsum me [55-65]

>>>>

% ---

\chooselang
{\chapter[Appendix A]{Since this page is not being completely filled, it is generating the bottom bottom of the page}}
{\chapter[Apêndice A]{Como esta página não está sendo completamente preenchida, ele está gerando a caixa inferior inferior da página}}
% ---

% Multiple-language document - babel - selectlanguage vs begin/end{otherlanguage}
% https://tex.stackexchange.com/questions/36526/multiple-language-document-babel-selectlanguage-vs-begin-endotherlanguage
\begin{otherlanguage*}{english}

@@

1. How to display the font size in use in the final output,
2. How to display the font size in use in the final output,
3. How to display the font size in use in the final output,
4. How to display the font size in use in the final output,
5. How to display the font size in use in the final output,
6. How to display the font size in use in the final output,
7. How to display the font size in use in the final output,
8. How to display the font size in use in the final output,
9. How to display the font size in use in the final output,

% As this page is not being completely filled, it is generating the page bottom bad box.
% Fix Underfull \vbox (badness 10000) has occurred while \output is active
%
% \flushbottom vs \raggedbottom
% https://tex.stackexchange.com/questions/65355/flushbottom-vs-raggedbottom
\newpage

@@

Lipsum me [31-35]

\end{otherlanguage*}

### 2017-08-30 monograph/thesis/pretexto/epigrafe.tex
Updated the pretexto remaining templates with ufscthesisx.

@@

    \vspace*{\fill}
    \begin{flushright}
        \textit{``Assim como aquele pecado da juventude, este documento te perseguirá pelo resto da vida.''}\\Enio Valmor Kassick
    \end{flushright}
    \begin{flushright}
        \textit{``Estupidez trará mais autoconfiança do que o conhecimento e a bravura juntas.''}\\
        Adriano Ruseler
    \end{flushright}
    \begin{flushright}
        \textit{``Learn from yesterday, live for today, hope for tomorrow. The important thing is not to stop questioning.''}\\ Albert Einstein
    \end{flushright}
    \begin{flushright}
        \textit{``The true sign of intelligence is not knowledge but imagination.''}\\  Albert Einstein
    \end{flushright}
    \begin{flushright}
        \textit{``Peace cannot be kept by force; it can only be achieved by understanding.''}\\ Albert Einstein
    \end{flushright}
    \begin{flushright}
        \textit{``Whoever is careless with the truth in small matters cannot be trusted with important matters.''}\\    Albert Einstein
    \end{flushright}
    \begin{flushright}
        \textit{``Extraordinary claims require extraordinary evidence''}\\
        Carl Sagan
    \end{flushright}
    \begin{flushright}
        \textit{``Catholic, which I was until I reached the age of reason.''}\\
        George Carlin
    \end{flushright}
    \begin{flushright}
        \textit{``We made too many wrong mistakes.''}\\
        Yogi Berra
    \end{flushright}

>>>>

\addtotextpreliminarycontent{\chooselang{Epigraph}{Epigrafe}}

@@

\vspace*{\fill}\chooselang
{
    \begin{flushright}
        \textit{``Learn from yesterday, live for today, hope for tomorrow. The important thing is not to stop questioning.''} \\ Albert Einstein
    \end{flushright}
    \begin{flushright}
        \textit{``The true sign of intelligence is not knowledge but imagination.''} \\  Albert Einstein
    \end{flushright}
    \begin{flushright}
        \textit{``Peace cannot be kept by force; it can only be achieved by understanding.''} \\ Albert Einstein
    \end{flushright}
    \begin{flushright}
        \textit{``Whoever is careless with the truth in small matters cannot be trusted with important matters.''} \\ Albert Einstein
    \end{flushright}
    \begin{flushright}
        \textit{``Extraordinary claims require extraordinary evidence''} \\ Carl Sagan
    \end{flushright}
    \begin{flushright}
        \textit{``Catholic, which I was until I reached the age of reason.''} \\ George Carlin
    \end{flushright}
    \begin{flushright}
        \textit{``We made too many wrong mistakes.''} \\ Yogi Berra
    \end{flushright}
}
{
    \begin{flushright}
        \textit{``Assim como aquele pecado da juventude, este documento te perseguirá pelo resto da vida. \showfont''} \\ Enio Valmor Kassick
    \end{flushright}
    \begin{flushright}
        \textit{``Estupidez trará mais autoconfiança do que o conhecimento e a bravura juntas.''} \\ Adriano Ruseler
    \end{flushright}
}

### 2017-08-30 monograph/thesis/pretexto/fichacatalografica.tex
Updated the pretexto remaining templates with ufscthesisx.

        Catalogação na fonte pela Biblioteca Universitária da Universidade Federal de Santa Catarina.

        Arquivo compilado às \currenttime h do dia \today.

@@

                \hspace{0.5cm} \imprimirtitulo~:~\imprimirsubtitulo~/~\imprimirautor;
                orientador(a),~\imprimirorientador;~co\hyp{}orientador(a),~\imprimircoorientador
                ~--~\imprimirlocal,~\currenttime,~\imprimirdata.

@@

                \hspace{0.5cm} Inclui referências
                \bigskip

                \hspace{0.5cm}
                    1. Uma Palavra\hyp{}chave ~
                    2. Outra Palavra\hyp{}chave ~
                    3. Mais Palavras\hyp{}chave ~
                    I. \imprimirorientador ~
                    II. \imprimircoorientador ~
                    III. \imprimirprograma ~
                    IV. \imprimirtitulo ~
                \bigskip

>>>>

        \chooselang
        {Cataloging at source by the University Library of the Federal University of Santa Catarina.}
        {Catalogação na fonte pela Biblioteca Universitária da Universidade Federal de Santa Catarina.}

        \chooselang
        {File compiled at \currenttime h of the day \today.}
        {Arquivo compilado às \currenttime h do dia \today.}

@@

                \hspace{0.5cm} \imprimirtitulo~:~\imprimirsubtitulo~/~\imprimirautor;
                \imprimirorientadorRotulo,~\imprimirorientador;~\imprimircoorientadorRotulo,~\imprimircoorientador
                ~--~\imprimirlocal,~\currenttime,~\imprimirdata.

@@

                \hspace{0.5cm} \chooselang{Includes references}{Inclui referências}
                \bigskip

                \hspace{0.5cm}
                    \wordslistlabled{\chooselang{\palavraschaveingles}{\palavraschaveportugues}}
                    I. \imprimirorientador ~
                    II. \imprimircoorientador ~
                    III. \imprimirprograma ~
                    IV. \imprimirtitulo ~
                \bigskip

### 2017-08-30 monograph/thesis/pretexto/folhadeaprovacao.tex
Updated the pretexto remaining templates with ufscthesisx.

@@

        \begin{minipage}{\textwidth}
            Esta Tese foi julgada adequada para obtenção do Título de Doutor em Engenharia Elétrica, na área de concentração em Eletrônica de Potência e Acionamento Elétrico, e aprovada em sua forma final pelo Programa de Pós--Graduação em Engenharia Elétrica da Universidade Federal de Santa Catarina.
        \end{minipage}%

@@

    \assinatura{\textbf{Prof. Marcelo Lobo Heldwein, Dr.} \\ Coordenador do Programa de Pós--Graduação em Engenharia Elétrica}
    \assinatura{\textbf{\imprimirorientador} \\ Orientador \\ Universidade Federal de Santa Catarina -- UFSC}
    \assinatura{\textbf{\imprimircoorientador} \\ Coorientador \\ Universidade Federal de Santa Catarina -- UFSC}

    \newpage
    \begin{flushleft}
        \textbf{Banca Examinadora:}
    \end{flushleft}

%   \assinatura{\textbf{Prof. Enio Valmor Kassik, Dr.}  \\ Instituto Federal de Santa Catarina -- IFSC}
    \assinatura{\textbf{Prof. Arnaldo José Perin, Dr.} \\ Universidade Federal de Santa Catarina -- UFSC}
    \assinatura{\textbf{Prof. Denizar Cruz Martins, Dr.} \\ Universidade Federal de Santa Catarina -- UFSC}
%   \assinatura{\textbf{Prof. Marcelo Lobo Heldwein, Dr.} \\ Universidade Federal de Santa Catarina -- UFSC}
    \assinatura{\textbf{Prof. Roberto Francisco Coelho, Dr.} \\ Universidade Federal de Santa Catarina -- UFSC}
    \assinatura{\textbf{Prof. Samir Ahmad Mussa, Dr.} \\ Universidade Federal de Santa Catarina -- UFSC}
    \assinatura{\textbf{Prof. Telles Brunelli Lazzarin, Dr.} \\ Universidade Federal de Santa Catarina -- UFSC}

>>>>

\addtotextpreliminarycontent{\chooselang{Approval Sheet}{Folha de Aprovação}}

@@

        \begin{minipage}{\textwidth}
            \chooselang
            {
                This thesis was considered appropriate to obtain the Doctor 's Degree in Electrical Engineering, in the area of concentration in Power Electronics and Electrical Drive, and approved in its final form by the Post-Graduate Program in Electrical Engineering of the Federal University of Santa Catarina.
            }
            {
                Esta Tese foi julgada adequada para obtenção do Título de Doutor em Engenharia Elétrica, na área de concentração em Eletrônica de Potência e Acionamento Elétrico, e aprovada em sua forma final pelo Programa de Pós--Graduação em Engenharia Elétrica da Universidade Federal de Santa Catarina.
            }
        \end{minipage}%

@@

    \assinatura
    {
        \textbf{Prof. Marcelo Lobo Heldwein, Dr.} \\
        \chooselang{Coordinator of the}{Coordenador do} \imprimirprograma
    }

    \assinatura
    {
        \textbf{\imprimirorientador} \\ \imprimirorientadorRotulo \\
        \imprimirinstituicao~--~\imprimirinstituicaosigla
    }

    \assinatura
    {
        \textbf{\imprimircoorientador} \\ \imprimircoorientadorRotulo \\
        \imprimirinstituicao~--~\imprimirinstituicaosigla
    }

    \newpage
    \begin{flushleft}
        \textbf{\chooselang{Examination Board:}{Banca Examinadora:}}
    \end{flushleft}

    \assinatura{\textbf{Prof. Arnaldo José Perin, \chooselang{PhD.}{Dr.}} \\
    \imprimirinstituicao~--~\imprimirinstituicaosigla}

    \assinatura{\textbf{Prof. Denizar Cruz Martins, \chooselang{PhD.}{Dr.}} \\
    \imprimirinstituicao~--~\imprimirinstituicaosigla}

    \assinatura{\textbf{Prof. Roberto Francisco Coelho, \chooselang{PhD.}{Dr.}} \\
    \imprimirinstituicao~--~\imprimirinstituicaosigla}

    \assinatura{\textbf{Prof. Samir Ahmad Mussa, \chooselang{PhD.}{Dr.}} \\
    \imprimirinstituicao~--~\imprimirinstituicaosigla}

    \assinatura{\textbf{Prof. Telles Brunelli Lazzarin, \chooselang{PhD.}{Dr.}} \\
    \imprimirinstituicao~--~\imprimirinstituicaosigla}
